---
title: "Downloading 10x hgmm data"
author: "Lambda Moses"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Downloading 10x hgmm data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates how to download the hgmm data in the BUS format with this package.
```{r}
library(TENxhgmmBUS)
library(ExperimentHub)
```

See which datasets are available with this package.
```{r}
eh <- ExperimentHub()
listResources(eh, "TENxhgmmBUS")
```

In this vignette, we download the 100 cell dataset. The `force` argument will force redownload even if the files are already present.
```{r}
download_hgmm(".", dataset = "hgmm100", force = TRUE)
```

Which files are downloaded?
```{r}
list.files("./out_hgmm100")
```

These should be sufficient to construct a sparse matrix with package [`BUSpaRse`](https://github.com/BUStools/BUSpaRse). 
